---
title: "Micronucleus Test Analysis Report"
output:
  html_document:
    theme: cosmo
    toc: true
    toc_float: true
    toc_depth: 2
    number_sections: false
    df_print: paged
params:
  results: NA
  study_name: "Unknown Study"
  file_name: "Unknown File"
  control_group: 1
  sig_level: 0.05
  report_date: "2024-01-01"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(knitr)
```

<style>
  body {
    font-family: Arial, sans-serif;
    line-height: 1.6;
    max-width: 1200px;
    margin: 0 auto;
    padding: 20px;
  }
  h1, h2, h3 { color: #2c3e50; }
  table {
    width: 100%;
    border-collapse: collapse;
    margin: 20px 0;
  }
  th {
    background-color: #3498db;
    color: white;
    padding: 10px;
    text-align: left;
  }
  td {
    padding: 8px;
    border-bottom: 1px solid #ddd;
  }
  tr:hover { background-color: #f5f5f5; }
  .info-box {
    background-color: #e8f4f8;
    border-left: 4px solid #3498db;
    padding: 15px;
    margin: 20px 0;
  }
  .significant {
    background-color: #d4edda !important;
    font-weight: bold;
  }
  .summary-box {
    background-color: #fff3cd;
    border-left: 4px solid #ffc107;
    padding: 15px;
    margin: 20px 0;
  }
</style>

# Micronucleus Test Analysis Report

---

## Study Information

<div class="info-box">

**Study:** `r params$study_name`

**File:** `r params$file_name`

**Report Date:** `r params$report_date`

```{r study_metadata, results='asis'}
if (!is.null(params$results) && nrow(params$results) > 0) {
  if ("Study_Number" %in% names(params$results)) {
    cat(paste0("\n\n**Study Number:** ", unique(params$results$Study_Number)[1], "\n\n"))
  }
  if ("Test_Item" %in% names(params$results)) {
    cat(paste0("**Test Item:** ", unique(params$results$Test_Item)[1], "\n\n"))
  }
  if ("Species" %in% names(params$results)) {
    cat(paste0("**Species:** ", unique(params$results$Species)[1], "\n\n"))
  }
  if ("Sex" %in% names(params$results)) {
    cat(paste0("**Sex:** ", unique(params$results$Sex)[1], "\n\n"))
  }
}
```

**Generated by:** MN Test Analysis Dashboard (GTA Package)

</div>

---

## Analysis Parameters

<div class="info-box">

- **Control Group:** Group `r params$control_group`
- **Significance Level (α):** `r params$sig_level`
- **Statistical Test:** Mann-Whitney U test (Wilcoxon rank-sum test)
- **Multiple Testing Correction:** Holm-Bonferroni method
- **Distribution:** Exact

</div>

---

## Analysis Results

```{r results_table}
if (!is.null(params$results)) {
  # Format numeric columns
  results_formatted <- params$results

  # Remove metadata columns from display (shown in header instead)
  metadata_cols <- c("Study_Number", "Test_Item", "Species", "Sex")
  display_cols <- setdiff(names(results_formatted), metadata_cols)
  results_display <- results_formatted[, display_cols, drop = FALSE]

  numeric_cols <- sapply(results_display, is.numeric)
  results_display[numeric_cols] <- lapply(
    results_display[numeric_cols],
    function(x) round(x, 4)
  )

  # Create table with better formatting
  kable(
    results_display,
    caption = "Mann-Whitney U Test Results with Holm-Bonferroni Correction",
    format = "html",
    table.attr = "class='table table-striped table-hover'"
  )
} else {
  cat("<p style='color: red;'>No results available</p>")
}
```

<script>
// Highlight significant results
document.addEventListener('DOMContentLoaded', function() {
  const table = document.querySelector('table');
  if (table) {
    const rows = table.querySelectorAll('tbody tr');
    rows.forEach(row => {
      const cells = row.querySelectorAll('td');
      const lastCell = cells[cells.length - 1];
      if (lastCell && lastCell.textContent.trim() === '*') {
        row.classList.add('significant');
      }
    });
  }
});
</script>

---

## Summary

```{r summary, results='asis'}
if (!is.null(params$results)) {
  # Exclude control group (first row) and any rows without p-values from counting
  comparison_results <- params$results[!is.na(params$results$p_value), ]
  total_comparisons <- nrow(comparison_results)
  significant_results <- sum(comparison_results$Significance == "*", na.rm = TRUE)

  cat('<div class="summary-box">\n\n')
  cat(paste0("- **Total Comparisons:** ", total_comparisons, "\n\n"))
  cat(paste0("- **Significant Results:** ", significant_results, "\n\n"))
  cat(paste0("- **Non-Significant Results:** ", total_comparisons - significant_results, "\n\n"))

  if (significant_results > 0) {
    cat("\n### Significant Comparisons:\n\n")
    sig_results <- comparison_results[comparison_results$Significance == "*", ]
    cat("<ul>\n")
    for (i in 1:nrow(sig_results)) {
      # Show group name, p-value, and Holm threshold for transparency
      threshold_text <- if (!is.na(sig_results$local_ai[i])) {
        paste0(", threshold = ", round(sig_results$local_ai[i], 4))
      } else {
        ""
      }
      cat(paste0("<li><strong>Group ", sig_results$GroupNumber[i], " (", sig_results$GroupName[i], ")</strong>: ",
                 "p-value = ", round(sig_results$p_value[i], 4),
                 threshold_text, "</li>\n"))
    }
    cat("</ul>\n")
  } else {
    cat("\n**No significant results found at α = ", params$sig_level, "**\n\n")
  }

  cat('</div>\n\n')
}
```

---

## Statistical Method

### Mann-Whitney U Test

The **Mann-Whitney U Test** (also known as Wilcoxon rank-sum test) is a non-parametric test used to compare two independent groups. It tests whether the distributions of two groups differ by assessing whether the ranks of values differ between groups.

**Key features:**

- Does not assume normal distribution
- Robust to outliers
- Tests for differences in central tendency
- Uses exact distribution for accurate p-values

### Holm-Bonferroni Correction

The **Holm-Bonferroni Correction** is a step-down multiple testing procedure that controls the family-wise error rate. It is more powerful than the classic Bonferroni correction while maintaining strong control of Type I errors.

**Procedure:**

1. Order p-values from smallest to largest
2. Compare each p-value to α/(n-i+1) where i is the rank
3. Reject hypotheses until the first non-significant result

### Interpretation

<div class="info-box">

- A **significant result** (marked with \*) indicates that the treatment group differs significantly from the control group at the specified significance level (α = `r params$sig_level`).

- **P-values are adjusted** for multiple comparisons using the Holm-Bonferroni method to control the family-wise error rate.

- Rows highlighted in **green** indicate significant results.

</div>

---

## Data Description

```{r data_description, results='asis'}
if (!is.null(params$results)) {
  cat("<div class='info-box'>\n\n")

  # Extract control group (first row)
  control_row <- params$results[1, ]

  # Extract treatment/excluded groups (rows 2+)
  treatment_rows <- params$results[-1, ]

  cat("### Treatment Groups Analyzed:\n\n")
  cat("<ul>\n")
  for (i in 1:nrow(treatment_rows)) {
    cat(paste0("<li>", treatment_rows$GroupName[i],
               " (Group ", treatment_rows$GroupNumber[i], ")",
               " - n = ", treatment_rows$N[i],
               ", Median = ", round(treatment_rows$Median[i], 2),
               "</li>\n"))
  }
  cat("</ul>\n\n")

  # Control group info from first row
  cat(paste0("\n### Control Group:\n\n",
             "- **Group ", control_row$GroupNumber, " (", control_row$GroupName, ")**\n",
             "- **Sample Size:** ", control_row$N, "\n",
             "- **Median:** ", round(control_row$Median, 2), "\n",
             "- **Mean:** ", round(control_row$Mean, 2), "\n",
             "- **SD:** ", round(control_row$SD, 2), "\n"))

  cat("\n</div>\n\n")
}
```

---

## Notes

- This report was automatically generated from the MN Test Analysis Dashboard
- Results are based on exact Mann-Whitney U test with Holm-Bonferroni correction
- For questions about the analysis, consult a statistician
- Keep this report with your study documentation

---

<footer style="margin-top: 40px; padding-top: 20px; border-top: 2px solid #ddd; color: #666; font-size: 0.9em;">
<p><em>Report generated by MN Test Analysis Dashboard (GTA Package v1.0.0)</em></p>
<p><em>Date: `r format(Sys.time(), "%Y-%m-%d %H:%M:%S")`</em></p>
</footer>
