---
title: "Micronucleus Test Analysis Report"
output: pdf_document
params:
  results: NA
  study_name: "Unknown Study"
  file_name: "Unknown File"
  control_group: 1
  sig_level: 0.05
  report_date: "2024-01-01"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)
library(knitr)
```

## Study Information

**Study:** `r params$study_name`

**File:** `r params$file_name`

**Report Date:** `r params$report_date`

```{r study_metadata, results='asis'}
if (!is.null(params$results) && nrow(params$results) > 0) {
  if ("Study_Number" %in% names(params$results)) {
    cat(paste0("\n\n**Study Number:** ", unique(params$results$Study_Number)[1], "\n\n"))
  }
  if ("Test_Item" %in% names(params$results)) {
    cat(paste0("**Test Item:** ", unique(params$results$Test_Item)[1], "\n\n"))
  }
  if ("Species" %in% names(params$results)) {
    cat(paste0("**Species:** ", unique(params$results$Species)[1], "\n\n"))
  }
  if ("Sex" %in% names(params$results)) {
    cat(paste0("**Sex:** ", unique(params$results$Sex)[1], "\n\n"))
  }
}
```

---

## Analysis Parameters

- **Control Group:** Group `r params$control_group`
- **Significance Level (α):** `r params$sig_level`
- **Statistical Test:** Mann-Whitney U test (Wilcoxon rank-sum test)
- **Multiple Testing Correction:** Holm-Bonferroni method
- **Distribution:** Exact

---

## Analysis Results

```{r results_table}
if (!is.null(params$results)) {
  # Format numeric columns
  results_formatted <- params$results

  # Remove metadata columns from display (shown in header instead)
  metadata_cols <- c("Study_Number", "Test_Item", "Species", "Sex")
  display_cols <- setdiff(names(results_formatted), metadata_cols)
  results_display <- results_formatted[, display_cols, drop = FALSE]

  numeric_cols <- sapply(results_display, is.numeric)
  results_display[numeric_cols] <- lapply(
    results_display[numeric_cols],
    function(x) round(x, 4)
  )

  # Create table
  kable(
    results_display,
    caption = "Mann-Whitney U Test Results with Holm-Bonferroni Correction",
    booktabs = TRUE,
    longtable = TRUE
  )
} else {
  cat("No results available")
}
```

---

## Summary

```{r summary}
if (!is.null(params$results)) {
  # Exclude control group (first row) and any rows without p-values from counting
  comparison_results <- params$results[!is.na(params$results$p_value), ]
  total_comparisons <- nrow(comparison_results)
  significant_results <- sum(comparison_results$Significance == "*", na.rm = TRUE)

  cat(paste0("- **Total Comparisons:** ", total_comparisons, "\n"))
  cat(paste0("- **Significant Results:** ", significant_results, "\n"))
  cat(paste0("- **Non-Significant Results:** ", total_comparisons - significant_results, "\n"))

  if (significant_results > 0) {
    cat("\n### Significant Comparisons:\n\n")
    sig_results <- comparison_results[comparison_results$Significance == "*", ]
    for (i in 1:nrow(sig_results)) {
      # Show group name, p-value, and Holm threshold for transparency
      threshold_text <- if (!is.na(sig_results$local_ai[i])) {
        paste0(", threshold = ", round(sig_results$local_ai[i], 4))
      } else {
        ""
      }
      cat(paste0("- Group ", sig_results$GroupNumber[i], " (", sig_results$GroupName[i], ")",
                 ": p-value = ", round(sig_results$p_value[i], 4),
                 threshold_text, "\n"))
    }
  }
}
```

---

## Statistical Method

**Mann-Whitney U Test** (also known as Wilcoxon rank-sum test) is a non-parametric test used to compare two independent groups. It tests whether the distributions of two groups differ by assessing whether the ranks of values differ between groups.

**Holm-Bonferroni Correction** is a step-down multiple testing procedure that controls the family-wise error rate. It is more powerful than the classic Bonferroni correction while maintaining strong control of Type I errors.

**Interpretation:**
- A significant result (marked with *) indicates that the treatment group differs significantly from the control group at the specified significance level (α = `r params$sig_level`).
- P-values are adjusted for multiple comparisons using the Holm-Bonferroni method.

---

*Report generated by MN Test Analysis Dashboard*
